Spatial Analysis

### 2021-06-09 Scripts/spatial_analisis.Rmd
run interpolation for all species

  # --------------- #
  # Testing
  # print(paste(yr))
  # yr = 1976
  # --------------- #

@@

# Test me
# Needs variables in Control panel
# Test no data: "Alosa aestivalis", reg = "Northeast US Fall", yr = 1974 
tis(input_data = ocean_data, grid = grid_eez_df, taxa = spp[1], reg = "Northeast US Fall", yr = 1974)

@@

@@

@@

# taxa
# spp <- "Centropristis striata"

spp <- ocean_data %>% 
  filter(region %in% regions,
         spp != "NA") %>% 
  pull(spp) %>% 
  unique()

@@

# Run for a single region
# historic_tif <- bind_rows(
  # lapply(years,tis,input_data = ocean_data, grid = grid, taxa = "Centropristis striata", reg = regions[2])
# )

# # Simple for-loop for running both regions (seasons)
# for(r in 1:2){
#   
#   partial_df <- bind_rows(
#     lapply(years,tis,input_data = ocean_data, grid = grid, taxa = spp, reg = regions[r])
#   )
#   
#   if(r == 1){
#     historic_tif <- partial_df
#   }else{
#     historic_tif <- bind_rows(historic_tif,partial_df)
#   }
#   
# }

# Run for one species
    run_tis(input_data = ocean_data, grid = grid_eez_df, taxa = "Centropristis striata", years = years, reg = regions)

# Run for multiple species
    run_tis(input_data = ocean_data, grid = grid_eez_df, taxa = spp[1], years = years, reg = regions)

# Save data for future plotting
# write_csv(historic_tif,
          # paste0(my_path("R","Partial"),"interpolated_data.csv"))

# Show data in notebook
head(historic_tif,10) %>% 
   kable(
    format = "html",
    caption = "Extrapolated data") %>% 
  kableExtra::kable_minimal() %>% 
  kableExtra::kable_styling() %>%
  kableExtra:: scroll_box(width = "100%", height = "300px")

>>>>

  # --------------- #
  # Testing
  print(paste(yr))
  yr = 1976
  # --------------- #

@@

# Test me
# Needs variables in Control panel
# Test no data: "Alosa aestivalis", reg = "Northeast US Fall", yr = 1974 
tis(input_data = ocean_data, grid = grid_eez_df, taxa = "Illex illecebrosus", reg = "Northeast US Fall", yr = 1973)

lapply(years,tis,input_data = ocean_data, grid = grid_eez_df, taxa = "Illex illecebrosus", reg = regions[2])

@@

  return_msg <- paste("Interpolation done for", taxa)

  return(return_msg)

@@

# Test me
    # run_tis(input_data = ocean_data, grid = grid_eez_df, taxa = "Centropristis striata", years = years, reg = regions)

@@

# species list
spp <- ocean_data %>% 
  filter(region %in% regions,
         spp != "NA") %>% 
  pull(spp) %>% 
  unique()

# Double check runs

spp_runs <- tibble(taxa = (list.files(my_path("R","Partial/Interpolation")))) %>%
  mutate(
    taxa = str_remove(taxa, "tif_"),
    taxa = str_remove(taxa, ".csv"),
    taxa = str_replace(taxa, "_", " ")
  )

# Missing runs
spp <- tibble(taxa=spp) %>% 
  anti_join(spp_runs) %>% 
  pull(taxa)

@@

# single species run
# run_tis(input_data = ocean_data,
#         grid = grid_eez_df,
#         years = years,
#         reg = regions,
#         taxa = "Illex illecebrosus"
# )

# Run them all in parallel
parallel::mclapply(spp,
                   run_tis, 
                   input_data = ocean_data,
                   grid = grid_eez_df,
                   years = years,
                   reg = regions
)
